---
title: "Collaborators"
format: 
  html:
    self-contained: true
include-after: custom.js
---

```{=html}
<script src="https://cdnjs.cloudflare.com/ajax/libs/jspdf/1.5.3/jspdf.min.js"></script>
<script src="https://cdnjs.cloudflare.com/ajax/libs/html2canvas/1.4.1/html2canvas.min.js"></script>
```
```{r include=FALSE}
library(cpaltemplates)
library(tidyverse)
library(sf)
library(leaflet)
library(googlesheets4)
library(highcharter)

impact <- read_sheet("https://docs.google.com/spreadsheets/d/1TInROva7mCNM7qvTA-6GFrkA4zIHcYNpy2eGhsgyg-8/edit#gid=0")

##### Filter/Transform Impact Data #####
impact$date <- ymd(impact$date)

start_date <- as.Date("2024-01-01")
current_date <- lubridate::floor_date(lubridate::today(), "month") - lubridate::days(1)

# Filter rows between January 1, 2024, and the current date
impact <- impact %>%
  filter(date >= start_date & date < current_date) %>%
  mutate(
    month_year = floor_date(date, "month"),
    formatted_month = format(month_year, "%B, %Y")
  )

impact$lbs_produce <- impact$bags * 10

##### Organization Data #####

### Oak Cliff Veggie ### 
oak_cliff_veggie <- impact %>%
  filter(partner == "Robbin Hood INC and Oak Cliff Veggie Project") 

ocv_lbs_trash <- sum(oak_cliff_veggie$lbs_trash, na.rm = TRUE)
ocv_lbs_produce <- sum(oak_cliff_veggie$lbs_produce, na.rm = TRUE)
ocv_people_served <- sum(oak_cliff_veggie$people_served, na.rm = TRUE)
ocv_events <- nrow(oak_cliff_veggie)

oak_cliff_veggie_cumsum <- oak_cliff_veggie %>%
  mutate(weight_of_impact = lbs_trash + lbs_produce) %>%
  group_by(formatted_month, month_year) %>%
  summarise(monthly_weight = sum(weight_of_impact)) %>%
  arrange(month_year) %>%
  group_by(month_year, formatted_month) %>%
  ungroup() %>%
  mutate(cumulative_weight = cumsum(monthly_weight))

### Robin Hood INC ### 
robin_hood_inc <- bind_rows(
  impact %>% filter(partner == "Robbin Hood INC"),
  oak_cliff_veggie) 

rh_lbs_trash <- sum(robin_hood_inc$lbs_trash, na.rm = TRUE)
rh_lbs_produce <- sum(robin_hood_inc$lbs_produce, na.rm = TRUE)
rh_people_served <- sum(robin_hood_inc$people_served, na.rm = TRUE)
rh_events <- nrow(robin_hood_inc)

robin_hood_cumsum <- robin_hood_inc %>%
  mutate(weight_of_impact = lbs_trash + lbs_produce) %>%
  group_by(formatted_month, month_year) %>%
  summarise(monthly_weight = sum(weight_of_impact)) %>%
  arrange(month_year) %>%
  ungroup() %>%
  mutate(cumulative_weight = cumsum(monthly_weight)) 
  
### Not My Son ### 
not_my_son <- impact %>%
  filter(partner == "Not My Son") 

nms_lbs_trash <- sum(not_my_son$lbs_trash, na.rm = TRUE)
nms_lbs_produce <- sum(not_my_son$lbs_produce, na.rm = TRUE)
nms_people_served <- sum(not_my_son$people_served, na.rm = TRUE)
nms_events <- nrow(not_my_son)

not_my_son_cumsum <- not_my_son %>%
  mutate(weight_of_impact = lbs_trash + lbs_produce) %>%
  group_by(formatted_month, month_year) %>%
  summarise(monthly_weight = sum(weight_of_impact)) %>%
  arrange(month_year) %>%
  ungroup() %>%
  mutate(cumulative_weight = cumsum(monthly_weight)) 

### United Peoples Coalition ###
united_peoples_coalition <- impact %>%
  filter(partner == "United Peoples Coalition") 

upc_lbs_trash <- sum(united_peoples_coalition$lbs_trash, na.rm = TRUE)
upc_lbs_produce <- sum(united_peoples_coalition$lbs_produce, na.rm = TRUE)
upc_people_served <- sum(united_peoples_coalition$people_served, na.rm = TRUE)
upc_events <- nrow(united_peoples_coalition)

united_cumsum <- united_peoples_coalition %>%
  mutate(weight_of_impact = lbs_trash + lbs_produce) %>%
  group_by(formatted_month, month_year) %>%
  summarise(monthly_weight = sum(weight_of_impact)) %>%
  arrange(month_year) %>%
  ungroup() %>%
  mutate(cumulative_weight = cumsum(monthly_weight)) 

### Goldmark Cultural Center ###
goldmark_cultural <- impact %>%
  filter(partner == "Goldmark Cultural Center") 

gcc_lbs_trash <- sum(goldmark_cultural$lbs_trash, na.rm = TRUE)
gcc_lbs_produce <- sum(goldmark_cultural$lbs_produce, na.rm = TRUE)
gcc_people_served <- sum(goldmark_cultural$people_served, na.rm = TRUE)
gcc_events <- nrow(goldmark_cultural)

goldmark_cumsum <- goldmark_cultural %>%
  mutate(weight_of_impact = lbs_trash + lbs_produce) %>%
  group_by(formatted_month, month_year) %>%
  summarise(monthly_weight = sum(weight_of_impact)) %>%
  arrange(month_year) %>%
  ungroup() %>%
  mutate(cumulative_weight = cumsum(monthly_weight)) 

### Pop Up Comfortt ###
pop_up_comfortt <- impact %>%
  filter(partner == "Pop Up Comfortt") 

pc_lbs_trash <- sum(pop_up_comfortt$lbs_trash, na.rm = TRUE)
pc_lbs_produce <- sum(pop_up_comfortt$lbs_produce, na.rm = TRUE)
pc_people_served <- sum(pop_up_comfortt$people_served, na.rm = TRUE)
pc_events <- nrow(pop_up_comfortt)

pop_up_cumsum <- pop_up_comfortt %>%
  mutate(weight_of_impact = lbs_trash + lbs_produce) %>%
  group_by(formatted_month, month_year) %>%
  summarise(monthly_weight = sum(weight_of_impact)) %>%
  arrange(month_year) %>%
  ungroup() %>%
  mutate(cumulative_weight = cumsum(monthly_weight)) 

### Serun Foundation ###
serun <- impact %>%
  filter(partner == "Serun Foundation") 
sf_lbs_trash <- sum(serun$lbs_trash, na.rm = TRUE)
sf_lbs_produce <- sum(serun$lbs_produce, na.rm = TRUE)
sf_people_served <- sum(serun$people_served, na.rm = TRUE)
sf_events <- nrow(serun)

serun_cumsum <- serun %>%
  mutate(weight_of_impact = lbs_trash + lbs_produce) %>%
  group_by(formatted_month, month_year) %>%
  summarise(monthly_weight = sum(weight_of_impact)) %>%
  arrange(month_year) %>%
  ungroup() %>%
  mutate(cumulative_weight = cumsum(monthly_weight)) 

### Bachman Lake Together ###
bachman_lt <- impact %>%
  filter(partner == "Bachman Lake Together") 
blt_lbs_trash <- sum(bachman_lt$lbs_trash, na.rm = TRUE)
blt_lbs_produce <- sum(bachman_lt$lbs_produce, na.rm = TRUE)
blt_people_served <- sum(bachman_lt$people_served, na.rm = TRUE)
blt_events <- nrow(bachman_lt)

serun_cumsum <- serun %>%
  mutate(weight_of_impact = lbs_trash + lbs_produce) %>%
  group_by(formatted_month, month_year) %>%
  summarise(monthly_weight = sum(weight_of_impact)) %>%
  arrange(month_year) %>%
  ungroup() %>%
  mutate(cumulative_weight = cumsum(monthly_weight)) 

##### Map Data #####
point_data <- st_read("data/CPTED_assessment_location.gpkg")

geojson_data <- st_read("data/dpd_divisions.geojson")

rtm_cells_1 <- st_read("data/rtm_cells/citywide_rtm.shp")

polygons <- st_transform(geojson_data, crs = 4269)

rtm_cells <- st_transform(rtm_cells_1, crs = 4269)

date_format <- "%m/%d/%Y"

point_data$Date.Deployed <- as.Date(point_data$Date.Deployed, format = date_format)

# Calculate days since deployment
current_date <- Sys.Date()

point_data$Days.Since.Deployed <- as.numeric(difftime(current_date, point_data$Date.Deployed, units = "days"))

point_data$Days.Since.Deployed[is.na(point_data$Days.Since.Deployed)] <- 0

camera_towers <- point_data %>%
  filter(Days.Since.Deployed != 0 )

camera_towers_30 <-camera_towers %>%
  filter(Days.Since.Deployed <= 30 )

camera_towers_60 <- camera_towers %>%
  filter(Days.Since.Deployed <= 60 )

camera_towers_90 <- camera_towers %>%
  filter(Days.Since.Deployed <= 90 )

camera_towers_over_90 <- camera_towers %>%
  filter(Days.Since.Deployed > 90 )
```

```{=html}
<style>
  .map-container, .graph-container {
      position: relative;
      display: inline-block;
      border: 5px solid #042d33;
      padding: 1px;
      margin: 25px;
      width: 800px;  /* Set the desired width */
  }

  /* Add border to the entire tabset panel */
  .panel-tabset {
      border: 2px solid #ccc;
      padding: 15px;
      border-radius: 5px;
  }

  /* Add border to individual tabs */
  .nav-tabs > li > a {
      border: 1px solid #ccc;
      border-radius: 5px 5px 0 0;
      margin-right: 2px;
  }

  /* Add border and highlight to active tab */
  .nav-tabs > li.active > a {
      border-bottom-color: transparent;
      background-color: #f0f0f0;  /* Highlight active tab */
      color: #000;                /* Change text color of active tab */
  }

  /* Add border to tab content */
  .tab-content {
      border: 1px solid #ccc;
      border-top: none;
      padding: 15px;
      border-radius: 0 0 5px 5px;
  } 
    /* Print button styles */
  .print-button {
      background-color: #042d33;
      color: white;
      border: none;
      padding: 10px 20px;
      text-align: center;
      text-decoration: none;
      display: inline-block;
      font-size: 16px;
      margin: 20px 2px;
      cursor: pointer;
      border-radius: 5px;
  }

  .print-button:hover {
      background-color: #06414c;
  }
</style>

<script>
  document.addEventListener("DOMContentLoaded", function() {
      var tabs = document.querySelectorAll('.nav-tabs li a');

      tabs.forEach(function(tab) {
          tab.addEventListener('click', function(event) {
              event.preventDefault(); // Prevent the default behavior
              var targetId = this.getAttribute('href').substring(1);
              var targetElement = document.getElementById(targetId);

              if (targetElement) {
              // Scroll to the target element smoothly
              targetElement.scrollIntoView({ behavior: 'smooth' });
              }

              // Activate the clicked tab
              tabs.forEach(function(t) {
                  t.parentElement.classList.remove('active');
              });
              this.parentElement.classList.add('active');

              // Show the corresponding tab content
              var tabContents = document.querySelectorAll('.tab-content .tab-pane');
              tabContents.forEach(function(content) {
                  content.classList.remove('active');
              });
              targetElement.classList.add('active');
          });
      });

               // Add event listener for download PDF button
      document.getElementById('download-pdf').addEventListener('click', function() {
              // Get the active tab content
              var activeTabContent = document.querySelector('.tab-pane.active');

            html2canvas(activeTabContent).then(function(canvas) {
                var imgData = canvas.toDataURL('image/png');
                var pdf = new jsPDF('p', 'pt', 'a4');
                var margin = 20;
                var imgWidth = pdf.internal.pageSize.getWidth() - margin * 2;
                var pageHeight = pdf.internal.pageSize.getHeight();  
                var imgHeight = canvas.height * imgWidth / canvas.width;
                var heightLeft = imgHeight;

                var position = margin;

                pdf.addImage(imgData, 'PNG', margin, position, imgWidth, imgHeight);
                heightLeft -= pageHeight;

                while (heightLeft >= 0) {
                    position = heightLeft - imgHeight - margin;
                    pdf.addPage();
                    pdf.addImage(imgData, 'PNG', margin, position, imgWidth, imgHeight);
                    heightLeft -= pageHeight;
                }

                pdf.save('download.pdf');
          });
      });
  });
      
</script>
```
## Dallas OIPSS {#Dallas-OIPSS}

::: grid
::: g-col-12
The Office of Integrated Public Safety Solutions (OIPSS) was created in April 2020. Under the R.E.A.L. Change Initiative implemented by the City Manager, the OIPSS works proactively to address systemic factors that contribute to criminal activity by providing non-law enforcement solutions that improve the quality of life in the community and reduce the demand for police service.
:::
:::

### CPTED {style="color: white"}

::: grid
::: {.g-col-12 style="color: black;"}
Crime Prevention Through Environmental Design or CPTED (pronounced sep-ted) suggests that the design of buildings, landscaping and outdoor environments can either encourage or discourage crime. CPTED attempts to minimize crime and the fear of crime by reducing criminal opportunity and fostering positive social interaction among the users of a space. The proper design and effective use of the built environment, can lead to a reduction in the fear of crime and the incidence of crime, and to improvement in the quality of life. The three elements of CPTED are Territoriality, Surveillance and Access Control. When used together, these elements strengthen total premise security and personal safety.
:::
:::

::: grid
::: g-col-12
::: map-container
```{r}

leaflet(data = point_data) %>%
  addTiles(urlTemplate = cpaltemplates::cpal_mapbox_color,
           attribution = cpaltemplates::cpal_leaflet) %>%
  addPolygons(data = polygons,
              group = "DPD Divisions",
              color = "#042d33",
              weight = 1.5,
              opacity = 1,
              fill = FALSE,
              layerId = ~row.names(polygons)) %>%
  addPolygons(data = rtm_cells,
              group = "RTM Risk Cells",
              color = "#042d33",
              weight = 1.5,
              opacity = 1,
              fill = FALSE,
              layerId = ~row.names(rtm_cells)) %>%
  addAwesomeMarkers(
    lng = ~location.x,
    lat = ~location.y,
    group = "Assessment Locations",
    label = ~paste("<b>Location:</b>", point_data$Location) %>%
      lapply(htmltools::HTML),
    icon = awesomeIcons(
      library = "fa",
      icon = "building",
      iconColor = '#FFFFFF',
      markerColor = 'cadetblue'
    )) %>%
   addAwesomeMarkers(
    lng = ~camera_towers_30$location.x,
    lat = ~camera_towers_30$location.y,
    group = "Camera Towers",
    label = ~paste("<b>Location:</b>", camera_towers$Location, "<br><b>Date Deployed:</b>",  camera_towers_30$Date.Deployed, "<br><b>Days Since Deployed:</b>", camera_towers_30$Days.Since.Deployed) %>%
      lapply(htmltools::HTML),
    icon = awesomeIcons(
      library = "fa",
      icon = "camera",
      iconColor = '#FFFFFF',
      markerColor = 'yellow')
   ) %>%
     addAwesomeMarkers(
    lng = ~camera_towers_60$location.x,
    lat = ~camera_towers_60$location.y,
    group = "Camera Towers",
    label = ~paste("<b>Location:</b>", camera_towers$Location, "<br><b>Date Deployed:</b>",  camera_towers_60$Date.Deployed, "<br><b>Days Since Deployed:</b>", camera_towers_60$Days.Since.Deployed) %>%
      lapply(htmltools::HTML),
    icon = awesomeIcons(
      library = "fa",
      icon = "camera",
      iconColor = '#FFFFFF',
      markerColor = 'orange')
   ) %>%
     addAwesomeMarkers(
    lng = ~camera_towers_90$location.x,
    lat = ~camera_towers_90$location.y,
    group = "Camera Towers",
    label = ~paste("<b>Location:</b>", camera_towers$Location, "<br><b>Date Deployed:</b>",  camera_towers_90$Date.Deployed, "<br><b>Days Since Deployed:</b>", camera_towers_90$Days.Since.Deployed) %>%
      lapply(htmltools::HTML),
    icon = awesomeIcons(
      library = "fa",
      icon = "camera",
      iconColor = '#FFFFFF',
      markerColor = 'red')
   ) %>%
     addAwesomeMarkers(
    lng = ~camera_towers_over_90$location.x,
    lat = ~camera_towers_over_90$location.y,
    group = "Camera Towers",
    label = ~paste("<b>Location:</b>", camera_towers$Location, "<br><b>Date Deployed:</b>",  camera_towers_over_90$Date.Deployed, "<br><b>Days Since Deployed:</b>", camera_towers_over_90$Days.Since.Deployed) %>%
      lapply(htmltools::HTML),
    icon = awesomeIcons(
      library = "fa",
      icon = "camera",
      iconColor = '#FFFFFF',
      markerColor = 'brown')
   ) %>%
  addLayersControl(
    overlayGroups = c("Assessment Locations", "Camera Towers", "RTM Risk Cells"),
    options = layersControlOptions(collapsed = FALSE)
  ) 

  

```
:::
:::
:::

## Community Partners

::: grid
::: g-col-12
::: panel-tabset
### Not My Son
::: grid
::: g-col-12
```{=html}
<p style="text-align: center;font-weight: bold;">Contributions of Not My Son</p>
```
:::
:::

::: grid
::: g-col-3
```{r}
nms_lbs_trash <- formatC(nms_lbs_trash, format = "d", big.mark = ",")
html_code <- paste0(
  '<div style="display: flex; flex-direction: column; align-items: center; height: 150px; border: 1px solid #042d33; border-radius: 5px; background-color: #042d33; color: white; position: relative;">',
  '<div style="position: absolute; top: 15%; width: 100%; display: flex; flex-direction: column; align-items: center;">',
  '<div style="display: flex; align-items: center; font-size: 2em; font-weight: bold;">', 
  nms_lbs_trash, 
  '<span style="font-size: 1.25em; margin-left: 10px;">', bsicons::bs_icon("trash"), '</span></div>',
  '</div>',
  '<div style="position: absolute; bottom: 20px; width: 100%; text-align: center;">Pounds of Trash Removed</div>',
  '</div>'
)
htmltools::HTML(html_code)
```
:::

::: g-col-3
```{r}
nms_lbs_produce <- formatC(nms_lbs_produce, format = "d", big.mark = ",")
html_code <- paste0(
  '<div style="display: flex; flex-direction: column; align-items: center; height: 150px; border: 1px solid #042d33; border-radius: 5px; background-color: #042d33; color: white; position: relative;">',
  '<div style="position: absolute; top: 15%; width: 100%; display: flex; flex-direction: column; align-items: center;">',
  '<div style="display: flex; align-items: center; font-size: 2em; font-weight: bold;">', 
  nms_lbs_produce, 
  '<span style="font-size: 1.25em; margin-left: 10px;">', bsicons::bs_icon("basket2"), '</span></div>',
  '</div>',
  '<div style="position: absolute; bottom: 20px; width: 100%; text-align: center;">Pounds of Produce Distributed</div>',
  '</div>'
)
htmltools::HTML(html_code)
```
:::

::: g-col-3
```{r}
nms_average_people_served <- formatC(nms_people_served, format = "d", big.mark = ",")
html_code <- paste0(
  '<div style="display: flex; flex-direction: column; align-items: center; height: 150px; border: 1px solid #042d33; border-radius: 5px; background-color: #042d33; color: white; position: relative;">',
  '<div style="position: absolute; top: 15%; width: 100%; display: flex; flex-direction: column; align-items: center;">',
  '<div style="display: flex; align-items: center; font-size: 2em; font-weight: bold;">', 
  nms_people_served, 
  '<span style="font-size: 1.25em; margin-left: 10px;">', bsicons::bs_icon("person"), '</span></div>',
  '</div>',
  '<div style="position: absolute; bottom: 20px; width: 100%; text-align: center;">Individuals Served at Produce Drives</div>',
  '</div>'
)
htmltools::HTML(html_code)
```
:::

::: g-col-3
```{r}
html_code <- paste0(
  '<div style="display: flex; flex-direction: column; align-items: center; height: 150px; border: 1px solid #042d33; border-radius: 5px; background-color: #042d33; color: white; position: relative;">',
  '<div style="position: absolute; top: 15%; width: 100%; display: flex; flex-direction: column; align-items: center;">',
  '<div style="display: flex; align-items: center; font-size: 2em; font-weight: bold;">', 
  nms_events, 
  '<span style="font-size: 1.25em; margin-left: 10px;">', bsicons::bs_icon("hammer"), '</span></div>',
  '</div>',
  '<div style="position: absolute; bottom: 20px; width: 100%; text-align: center;">D.I.C.E Events Supported</div>',
  '</div>'
)
htmltools::HTML(html_code)
```
:::
:::

::: grid
::: g-col-12
```{r}
highchart() %>%
  hc_chart(type = "line") %>%
  hc_xAxis(categories = not_my_son_cumsum$formatted_month) %>%
  hc_yAxis(min = 0) %>% 
  hc_add_series(data = not_my_son_cumsum$cumulative_weight, name = "Pounds", x = not_my_son$formatted_month) %>%
  hc_title(text = "Cumulative Weight of Impact") %>%
  hc_subtitle(text = "by Not My Son") %>%
  hc_tooltip(pointFormat = "{series.name}: {point.y:2f}") %>%
  hc_colors(palette_cpal_main) %>%
  hc_plotOptions(series = list(
    lineWidth = 4,  
    marker = list(
      enabled = TRUE,
      symbol = "circle", 
      radius = 6,         
      fillColor = NULL,   
      lineWidth = 2,
      lineColor = NULL    
    )
  )) |> 
  hc_legend(enabled = FALSE)


```
:::
:::

### Robin Hood INC

::: grid
::: g-col-12
```{=html}
<p style="text-align: center;font-weight: bold;">Contributions of Robin Hood INC</p>
```
:::
:::

::: grid
::: g-col-3
```{r}
rh_lbs_trash <- formatC(rh_lbs_trash, format = "d", big.mark = ",")
html_code <- paste0(
  '<div style="display: flex; flex-direction: column; align-items: center; height: 150px; border: 1px solid #042d33; border-radius: 5px; background-color: #042d33; color: white; position: relative;">',
  '<div style="position: absolute; top: 15%; width: 100%; display: flex; flex-direction: column; align-items: center;">',
  '<div style="display: flex; align-items: center; font-size: 2em; font-weight: bold;">', 
  rh_lbs_trash, 
  '<span style="font-size: 1.25em; margin-left: 10px;">', bsicons::bs_icon("trash"), '</span></div>',
  '</div>',
  '<div style="position: absolute; bottom: 20px; width: 100%; text-align: center;">Pounds of Trash Removed</div>',
  '</div>'
)
htmltools::HTML(html_code)
```
:::

::: g-col-3
```{r}
rh_lbs_produce <- formatC(rh_lbs_produce, format = "d", big.mark = ",")
html_code <- paste0(
  '<div style="display: flex; flex-direction: column; align-items: center; height: 150px; border: 1px solid #042d33; border-radius: 5px; background-color: #042d33; color: white; position: relative;">',
  '<div style="position: absolute; top: 15%; width: 100%; display: flex; flex-direction: column; align-items: center;">',
  '<div style="display: flex; align-items: center; font-size: 2em; font-weight: bold;">', 
  rh_lbs_produce, 
  '<span style="font-size: 1.25em; margin-left: 10px;">', bsicons::bs_icon("basket2"), '</span></div>',
  '</div>',
  '<div style="position: absolute; bottom: 20px; width: 100%; text-align: center;">Pounds of Produce Distributed</div>',
  '</div>'
)
htmltools::HTML(html_code)
```
:::

::: g-col-3
```{r}
rh_average_people_served <- formatC(rh_people_served, format = "d", big.mark = ",")
html_code <- paste0(
  '<div style="display: flex; flex-direction: column; align-items: center; height: 150px; border: 1px solid #042d33; border-radius: 5px; background-color: #042d33; color: white; position: relative;">',
  '<div style="position: absolute; top: 15%; width: 100%; display: flex; flex-direction: column; align-items: center;">',
  '<div style="display: flex; align-items: center; font-size: 2em; font-weight: bold;">', 
  rh_people_served, 
  '<span style="font-size: 1.25em; margin-left: 10px;">', bsicons::bs_icon("person"), '</span></div>',
  '</div>',
  '<div style="position: absolute; bottom: 20px; width: 100%; text-align: center;">Individuals Served at Produce Drives</div>',
  '</div>'
)
htmltools::HTML(html_code)
```
:::

::: g-col-3
```{r}
html_code <- paste0(
  '<div style="display: flex; flex-direction: column; align-items: center; height: 150px; border: 1px solid #042d33; border-radius: 5px; background-color: #042d33; color: white; position: relative;">',
  '<div style="position: absolute; top: 15%; width: 100%; display: flex; flex-direction: column; align-items: center;">',
  '<div style="display: flex; align-items: center; font-size: 2em; font-weight: bold;">', 
  rh_events, 
  '<span style="font-size: 1.25em; margin-left: 10px;">', bsicons::bs_icon("hammer"), '</span></div>',
  '</div>',
  '<div style="position: absolute; bottom: 20px; width: 100%; text-align: center;">D.I.C.E Events Supported</div>',
  '</div>'
)
htmltools::HTML(html_code)
```
:::
:::

::: grid
::: g-col-12
```{r}
highchart() %>%
  hc_chart(type = "line") %>%
  hc_xAxis(categories = robin_hood_cumsum$formatted_month) %>%
  hc_yAxis(min = 0) %>% 
  hc_add_series(data = robin_hood_cumsum$cumulative_weight, name = "Pounds", x = robin_hood_cumsum$formatted_month) %>%
  hc_title(text = "Cumulative Weight of Impact") %>%
  hc_subtitle(text = "by Robin Hood INC") %>%
  hc_tooltip(pointFormat = "{series.name}: {point.y:2f}") %>%
  hc_colors(palette_cpal_main) %>%
  hc_plotOptions(series = list(
    lineWidth = 4,  
    marker = list(
      enabled = TRUE,
      symbol = "circle", 
      radius = 6,         
      fillColor = NULL,   
      lineWidth = 2,
      lineColor = NULL    
    )
  )) |> 
  hc_legend(enabled = FALSE)


```
:::
:::

### Serun Foundation

::: grid
::: g-col-12
```{=html}
<p style="text-align: center;font-weight: bold;">Contributions of the Serun Foundation</p>
```
:::
:::

::: grid
::: g-col-3
```{r}
sf_lbs_trash <- formatC(sf_lbs_trash, format = "d", big.mark = ",")
html_code <- paste0(
  '<div style="display: flex; flex-direction: column; align-items: center; height: 150px; border: 1px solid #042d33; border-radius: 5px; background-color: #042d33; color: white; position: relative;">',
  '<div style="position: absolute; top: 15%; width: 100%; display: flex; flex-direction: column; align-items: center;">',
  '<div style="display: flex; align-items: center; font-size: 2em; font-weight: bold;">', 
  sf_lbs_trash, 
  '<span style="font-size: 1.25em; margin-left: 10px;">', bsicons::bs_icon("trash"), '</span></div>',
  '</div>',
  '<div style="position: absolute; bottom: 20px; width: 100%; text-align: center;">Pounds of Trash Removed</div>',
  '</div>'
)
htmltools::HTML(html_code)
```
:::

::: g-col-3
```{r}
sf_lbs_produce <- formatC(sf_lbs_produce, format = "d", big.mark = ",")
html_code <- paste0(
  '<div style="display: flex; flex-direction: column; align-items: center; height: 150px; border: 1px solid #042d33; border-radius: 5px; background-color: #042d33; color: white; position: relative;">',
  '<div style="position: absolute; top: 15%; width: 100%; display: flex; flex-direction: column; align-items: center;">',
  '<div style="display: flex; align-items: center; font-size: 2em; font-weight: bold;">', 
  sf_lbs_produce, 
  '<span style="font-size: 1.25em; margin-left: 10px;">', bsicons::bs_icon("basket2"), '</span></div>',
  '</div>',
  '<div style="position: absolute; bottom: 20px; width: 100%; text-align: center;">Pounds of Produce Distributed</div>',
  '</div>'
)
htmltools::HTML(html_code)
```
:::

::: g-col-3
```{r}
sf_average_people_served <- formatC(sf_people_served, format = "d", big.mark = ",")
html_code <- paste0(
  '<div style="display: flex; flex-direction: column; align-items: center; height: 150px; border: 1px solid #042d33; border-radius: 5px; background-color: #042d33; color: white; position: relative;">',
  '<div style="position: absolute; top: 15%; width: 100%; display: flex; flex-direction: column; align-items: center;">',
  '<div style="display: flex; align-items: center; font-size: 2em; font-weight: bold;">', 
  sf_people_served, 
  '<span style="font-size: 1.25em; margin-left: 10px;">', bsicons::bs_icon("person"), '</span></div>',
  '</div>',
  '<div style="position: absolute; bottom: 20px; width: 100%; text-align: center;">Individuals Served at Produce Drives</div>',
  '</div>'
)
htmltools::HTML(html_code)
```
:::

::: g-col-3
```{r}
html_code <- paste0(
  '<div style="display: flex; flex-direction: column; align-items: center; height: 150px; border: 1px solid #042d33; border-radius: 5px; background-color: #042d33; color: white; position: relative;">',
  '<div style="position: absolute; top: 15%; width: 100%; display: flex; flex-direction: column; align-items: center;">',
  '<div style="display: flex; align-items: center; font-size: 2em; font-weight: bold;">', 
  sf_events, 
  '<span style="font-size: 1.25em; margin-left: 10px;">', bsicons::bs_icon("hammer"), '</span></div>',
  '</div>',
  '<div style="position: absolute; bottom: 20px; width: 100%; text-align: center;">D.I.C.E Events Supported</div>',
  '</div>'
)
htmltools::HTML(html_code)
```
:::
:::

::: grid
::: g-col-12
```{r}

highchart() %>%
  hc_chart(type = "line") %>%
  hc_xAxis(categories = serun_cumsum$formatted_month) %>%
  hc_yAxis(min = 0) %>% 
  hc_add_series(data = serun_cumsum$cumulative_weight, name = "Pounds", x = serun_cumsum$formatted_month) %>%
  hc_title(text = "Cumulative Weight of Impact") %>%
  hc_subtitle(text = "by the Serun Foundation") %>%
  hc_tooltip(pointFormat = "{series.name}: {point.y:2f}") %>%
  hc_colors(palette_cpal_main) %>%
  hc_plotOptions(series = list(
    lineWidth = 4,  
    marker = list(
      enabled = TRUE,
      symbol = "circle", 
      radius = 6,         
      fillColor = NULL,   
      lineWidth = 2,
      lineColor = NULL    
    )
  )) |> 
  hc_legend(enabled = FALSE)

```
:::
:::

### United Peoples Coalition

::: grid
::: g-col-12
```{=html}
<p style="text-align: center;font-weight: bold;">Contributions of the United Peoples Coalition</p>
```
:::
:::

::: grid
::: g-col-3
```{r}
upc_lbs_trash <- formatC(upc_lbs_trash, format = "d", big.mark = ",")
html_code <- paste0(
  '<div style="display: flex; flex-direction: column; align-items: center; height: 150px; border: 1px solid #042d33; border-radius: 5px; background-color: #042d33; color: white; position: relative;">',
  '<div style="position: absolute; top: 15%; width: 100%; display: flex; flex-direction: column; align-items: center;">',
  '<div style="display: flex; align-items: center; font-size: 2em; font-weight: bold;">', 
  upc_lbs_trash, 
  '<span style="font-size: 1.25em; margin-left: 10px;">', bsicons::bs_icon("trash"), '</span></div>',
  '</div>',
  '<div style="position: absolute; bottom: 20px; width: 100%; text-align: center;">Pounds of Trash Removed</div>',
  '</div>'
)
htmltools::HTML(html_code)
```
:::

::: g-col-3
```{r}
upc_lbs_produce <- formatC(upc_lbs_produce, format = "d", big.mark = ",")
html_code <- paste0(
  '<div style="display: flex; flex-direction: column; align-items: center; height: 150px; border: 1px solid #042d33; border-radius: 5px; background-color: #042d33; color: white; position: relative;">',
  '<div style="position: absolute; top: 15%; width: 100%; display: flex; flex-direction: column; align-items: center;">',
  '<div style="display: flex; align-items: center; font-size: 2em; font-weight: bold;">', 
  upc_lbs_produce, 
  '<span style="font-size: 1.25em; margin-left: 10px;">', bsicons::bs_icon("basket2"), '</span></div>',
  '</div>',
  '<div style="position: absolute; bottom: 20px; width: 100%; text-align: center;">Pounds of Produce Distributed</div>',
  '</div>'
)
htmltools::HTML(html_code)
```
:::

::: g-col-3
```{r}
upc_average_people_served <- formatC(upc_people_served, format = "d", big.mark = ",")
html_code <- paste0(
  '<div style="display: flex; flex-direction: column; align-items: center; height: 150px; border: 1px solid #042d33; border-radius: 5px; background-color: #042d33; color: white; position: relative;">',
  '<div style="position: absolute; top: 15%; width: 100%; display: flex; flex-direction: column; align-items: center;">',
  '<div style="display: flex; align-items: center; font-size: 2em; font-weight: bold;">', 
  upc_people_served, 
  '<span style="font-size: 1.25em; margin-left: 10px;">', bsicons::bs_icon("person"), '</span></div>',
  '</div>',
  '<div style="position: absolute; bottom: 20px; width: 100%; text-align: center;">Individuals Served at Produce Drives</div>',
  '</div>'
)
htmltools::HTML(html_code)
```
:::

::: g-col-3
```{r}
html_code <- paste0(
  '<div style="display: flex; flex-direction: column; align-items: center; height: 150px; border: 1px solid #042d33; border-radius: 5px; background-color: #042d33; color: white; position: relative;">',
  '<div style="position: absolute; top: 15%; width: 100%; display: flex; flex-direction: column; align-items: center;">',
  '<div style="display: flex; align-items: center; font-size: 2em; font-weight: bold;">', 
  upc_events, 
  '<span style="font-size: 1.25em; margin-left: 10px;">', bsicons::bs_icon("hammer"), '</span></div>',
  '</div>',
  '<div style="position: absolute; bottom: 20px; width: 100%; text-align: center;">D.I.C.E Events Supported</div>',
  '</div>'
)
htmltools::HTML(html_code)
```
:::
:::

::: grid
::: g-col-12
```{r}

highchart() %>%
  hc_chart(type = "line") %>%
  hc_xAxis(categories = united_cumsum$formatted_month) %>%
  hc_yAxis(min = 0) %>% 
  hc_add_series(data = united_cumsum$cumulative_weight, name = "Pounds", x = united_cumsum$formatted_month) %>%
  hc_title(text = "Cumulative Weight of Impact") %>%
  hc_subtitle(text = "by the United Peoples Coalition") %>%
  hc_tooltip(pointFormat = "{series.name}: {point.y:2f}") %>%
  hc_colors(palette_cpal_main) %>%
  hc_plotOptions(series = list(
    lineWidth = 4,  
    marker = list(
      enabled = TRUE,
      symbol = "circle", 
      radius = 6,         
      fillColor = NULL,   
      lineWidth = 2,
      lineColor = NULL    
    )
  )) |> 
  hc_legend(enabled = FALSE)

```
:::
:::

### Bachman Lake Together

::: grid
::: g-col-12
```{=html}
<p style="text-align: center;font-weight: bold;">Contributions of Bachman Lake Together</p>
```
:::
:::

::: grid
::: g-col-3
```{r}
upc_lbs_trash <- formatC(blt_lbs_trash, format = "d", big.mark = ",")
html_code <- paste0(
  '<div style="display: flex; flex-direction: column; align-items: center; height: 150px; border: 1px solid #042d33; border-radius: 5px; background-color: #042d33; color: white; position: relative;">',
  '<div style="position: absolute; top: 15%; width: 100%; display: flex; flex-direction: column; align-items: center;">',
  '<div style="display: flex; align-items: center; font-size: 2em; font-weight: bold;">', 
  blt_lbs_trash, 
  '<span style="font-size: 1.25em; margin-left: 10px;">', bsicons::bs_icon("trash"), '</span></div>',
  '</div>',
  '<div style="position: absolute; bottom: 20px; width: 100%; text-align: center;">Pounds of Trash Removed</div>',
  '</div>'
)
htmltools::HTML(html_code)
```
:::

::: g-col-3
```{r}
upc_lbs_produce <- formatC(blt_lbs_produce, format = "d", big.mark = ",")
html_code <- paste0(
  '<div style="display: flex; flex-direction: column; align-items: center; height: 150px; border: 1px solid #042d33; border-radius: 5px; background-color: #042d33; color: white; position: relative;">',
  '<div style="position: absolute; top: 15%; width: 100%; display: flex; flex-direction: column; align-items: center;">',
  '<div style="display: flex; align-items: center; font-size: 2em; font-weight: bold;">', 
  blt_lbs_produce, 
  '<span style="font-size: 1.25em; margin-left: 10px;">', bsicons::bs_icon("basket2"), '</span></div>',
  '</div>',
  '<div style="position: absolute; bottom: 20px; width: 100%; text-align: center;">Pounds of Produce Distributed</div>',
  '</div>'
)
htmltools::HTML(html_code)
```
:::

::: g-col-3
```{r}
upc_average_people_served <- formatC(blt_people_served, format = "d", big.mark = ",")
html_code <- paste0(
  '<div style="display: flex; flex-direction: column; align-items: center; height: 150px; border: 1px solid #042d33; border-radius: 5px; background-color: #042d33; color: white; position: relative;">',
  '<div style="position: absolute; top: 15%; width: 100%; display: flex; flex-direction: column; align-items: center;">',
  '<div style="display: flex; align-items: center; font-size: 2em; font-weight: bold;">', 
  blt_people_served, 
  '<span style="font-size: 1.25em; margin-left: 10px;">', bsicons::bs_icon("person"), '</span></div>',
  '</div>',
  '<div style="position: absolute; bottom: 20px; width: 100%; text-align: center;">Individuals Served at Produce Drives</div>',
  '</div>'
)
htmltools::HTML(html_code)
```
:::

::: g-col-3
```{r}
html_code <- paste0(
  '<div style="display: flex; flex-direction: column; align-items: center; height: 150px; border: 1px solid #042d33; border-radius: 5px; background-color: #042d33; color: white; position: relative;">',
  '<div style="position: absolute; top: 15%; width: 100%; display: flex; flex-direction: column; align-items: center;">',
  '<div style="display: flex; align-items: center; font-size: 2em; font-weight: bold;">', 
  blt_events, 
  '<span style="font-size: 1.25em; margin-left: 10px;">', bsicons::bs_icon("hammer"), '</span></div>',
  '</div>',
  '<div style="position: absolute; bottom: 20px; width: 100%; text-align: center;">D.I.C.E Events Supported</div>',
  '</div>'
)
htmltools::HTML(html_code)
```
:::
:::

::: grid
::: g-col-12
```{r}

highchart() %>%
  hc_chart(type = "line") %>%
  hc_xAxis(categories = united_cumsum$formatted_month) %>%
  hc_yAxis(min = 0) %>% 
  hc_add_series(data = united_cumsum$cumulative_weight, name = "Pounds", x = united_cumsum$formatted_month) %>%
  hc_title(text = "Cumulative Weight of Impact") %>%
  hc_subtitle(text = "by Bachman Lake Together") %>%
  hc_tooltip(pointFormat = "{series.name}: {point.y:2f}") %>%
  hc_colors(palette_cpal_main) %>%
  hc_plotOptions(series = list(
    lineWidth = 4,  
    marker = list(
      enabled = TRUE,
      symbol = "circle", 
      radius = 6,         
      fillColor = NULL,   
      lineWidth = 2,
      lineColor = NULL    
    )
  )) |> 
  hc_legend(enabled = FALSE)

```
:::
:::

### Oak Cliff Veggie Project

::: grid
::: g-col-12
```{=html}
<p style="text-align: center;font-weight: bold;">Contributions of the Oak Cliff Veggie Project</p>
```
:::
:::

::: grid
::: g-col-3
```{r}
ocv_lbs_trash <- formatC(ocv_lbs_trash, format = "d", big.mark = ",")
html_code <- paste0(
  '<div style="display: flex; flex-direction: column; align-items: center; height: 150px; border: 1px solid #042d33; border-radius: 5px; background-color: #042d33; color: white; position: relative;">',
  '<div style="position: absolute; top: 15%; width: 100%; display: flex; flex-direction: column; align-items: center;">',
  '<div style="display: flex; align-items: center; font-size: 2em; font-weight: bold;">', 
  ocv_lbs_trash, 
  '<span style="font-size: 1.25em; margin-left: 10px;">', bsicons::bs_icon("trash"), '</span></div>',
  '</div>',
  '<div style="position: absolute; bottom: 20px; width: 100%; text-align: center;">Pounds of Trash Removed</div>',
  '</div>'
)
htmltools::HTML(html_code)
```
:::

::: g-col-3
```{r}
ocv_lbs_produce <- formatC(ocv_lbs_produce, format = "d", big.mark = ",")
html_code <- paste0(
  '<div style="display: flex; flex-direction: column; align-items: center; height: 150px; border: 1px solid #042d33; border-radius: 5px; background-color: #042d33; color: white; position: relative;">',
  '<div style="position: absolute; top: 15%; width: 100%; display: flex; flex-direction: column; align-items: center;">',
  '<div style="display: flex; align-items: center; font-size: 2em; font-weight: bold;">', 
  ocv_lbs_produce, 
  '<span style="font-size: 1.25em; margin-left: 10px;">', bsicons::bs_icon("basket2"), '</span></div>',
  '</div>',
  '<div style="position: absolute; bottom: 20px; width: 100%; text-align: center;">Pounds of Produce Distributed</div>',
  '</div>'
)
htmltools::HTML(html_code)
```
:::

::: g-col-3
```{r}
ocv_average_people_served <- formatC(ocv_people_served, format = "d", big.mark = ",")
html_code <- paste0(
  '<div style="display: flex; flex-direction: column; align-items: center; height: 150px; border: 1px solid #042d33; border-radius: 5px; background-color: #042d33; color: white; position: relative;">',
  '<div style="position: absolute; top: 15%; width: 100%; display: flex; flex-direction: column; align-items: center;">',
  '<div style="display: flex; align-items: center; font-size: 2em; font-weight: bold;">', 
  ocv_people_served, 
  '<span style="font-size: 1.25em; margin-left: 10px;">', bsicons::bs_icon("person"), '</span></div>',
  '</div>',
  '<div style="position: absolute; bottom: 20px; width: 100%; text-align: center;">Individuals Served at Produce Drives</div>',
  '</div>'
)
htmltools::HTML(html_code)
```
:::

::: g-col-3
```{r}
html_code <- paste0(
  '<div style="display: flex; flex-direction: column; align-items: center; height: 150px; border: 1px solid #042d33; border-radius: 5px; background-color: #042d33; color: white; position: relative;">',
  '<div style="position: absolute; top: 15%; width: 100%; display: flex; flex-direction: column; align-items: center;">',
  '<div style="display: flex; align-items: center; font-size: 2em; font-weight: bold;">', 
  ocv_events, 
  '<span style="font-size: 1.25em; margin-left: 10px;">', bsicons::bs_icon("hammer"), '</span></div>',
  '</div>',
  '<div style="position: absolute; bottom: 20px; width: 100%; text-align: center;">D.I.C.E Events Supported</div>',
  '</div>'
)
htmltools::HTML(html_code)
```
:::
:::

::: grid
::: g-col-12
```{r}

highchart() %>%
  hc_chart(type = "line") %>%
  hc_xAxis(categories = oak_cliff_veggie_cumsum$formatted_month) %>%
  hc_yAxis(min = 0) %>% 
  hc_add_series(data = oak_cliff_veggie_cumsum$cumulative_weight, name = "Pounds", x = oak_cliff_veggie_cumsum$formatted_month) %>%
  hc_title(text = "Cumulative Weight of Impact") %>%
  hc_subtitle(text = "by the Oak Cliff Veggie Project") %>%
  hc_tooltip(pointFormat = "{series.name}: {point.y:2f}") %>%
  hc_colors(palette_cpal_main) %>%
  hc_plotOptions(series = list(
    lineWidth = 4,  
    marker = list(
      enabled = TRUE,
      symbol = "circle", 
      radius = 6,         
      fillColor = NULL,   
      lineWidth = 2,
      lineColor = NULL    
    )
  )) |> 
  hc_legend(enabled = FALSE)

```
:::
:::

### Goldmark Cultural Center

::: grid
::: g-col-12
```{=html}
<p style="text-align: center;font-weight: bold;">Contributions of Goldmark Cultural Center</p>
```
:::
:::

::: grid
::: g-col-3
```{r}
gcc_lbs_trash <- formatC(gcc_lbs_trash, format = "d", big.mark = ",")
html_code <- paste0(
  '<div style="display: flex; flex-direction: column; align-items: center; height: 150px; border: 1px solid #042d33; border-radius: 5px; background-color: #042d33; color: white; position: relative;">',
  '<div style="position: absolute; top: 15%; width: 100%; display: flex; flex-direction: column; align-items: center;">',
  '<div style="display: flex; align-items: center; font-size: 2em; font-weight: bold;">', 
  gcc_lbs_trash, 
  '<span style="font-size: 1.25em; margin-left: 10px;">', bsicons::bs_icon("trash"), '</span></div>',
  '</div>',
  '<div style="position: absolute; bottom: 20px; width: 100%; text-align: center;">Pounds of Trash Removed</div>',
  '</div>'
)
htmltools::HTML(html_code)
```
:::

::: g-col-3
```{r}
gcc_lbs_produce <- formatC(gcc_lbs_produce, format = "d", big.mark = ",")
html_code <- paste0(
  '<div style="display: flex; flex-direction: column; align-items: center; height: 150px; border: 1px solid #042d33; border-radius: 5px; background-color: #042d33; color: white; position: relative;">',
  '<div style="position: absolute; top: 15%; width: 100%; display: flex; flex-direction: column; align-items: center;">',
  '<div style="display: flex; align-items: center; font-size: 2em; font-weight: bold;">', 
  gcc_lbs_produce, 
  '<span style="font-size: 1.25em; margin-left: 10px;">', bsicons::bs_icon("basket2"), '</span></div>',
  '</div>',
  '<div style="position: absolute; bottom: 20px; width: 100%; text-align: center;">Pounds of Produce Distributed</div>',
  '</div>'
)
htmltools::HTML(html_code)
```
:::

::: g-col-3
```{r}
gcc_people_served <- formatC(gcc_people_served, format = "d", big.mark = ",")
html_code <- paste0(
  '<div style="display: flex; flex-direction: column; align-items: center; height: 150px; border: 1px solid #042d33; border-radius: 5px; background-color: #042d33; color: white; position: relative;">',
  '<div style="position: absolute; top: 15%; width: 100%; display: flex; flex-direction: column; align-items: center;">',
  '<div style="display: flex; align-items: center; font-size: 2em; font-weight: bold;">', 
  gcc_people_served, 
  '<span style="font-size: 1.25em; margin-left: 10px;">', bsicons::bs_icon("person"), '</span></div>',
  '</div>',
  '<div style="position: absolute; bottom: 20px; width: 100%; text-align: center;">Individuals Served at Produce Drives</div>',
  '</div>'
)
htmltools::HTML(html_code)
```
:::

::: g-col-3
```{r}
html_code <- paste0(
  '<div style="display: flex; flex-direction: column; align-items: center; height: 150px; border: 1px solid #042d33; border-radius: 5px; background-color: #042d33; color: white; position: relative;">',
  '<div style="position: absolute; top: 15%; width: 100%; display: flex; flex-direction: column; align-items: center;">',
  '<div style="display: flex; align-items: center; font-size: 2em; font-weight: bold;">', 
  gcc_events, 
  '<span style="font-size: 1.25em; margin-left: 10px;">', bsicons::bs_icon("hammer"), '</span></div>',
  '</div>',
  '<div style="position: absolute; bottom: 20px; width: 100%; text-align: center;">D.I.C.E Events Supported</div>',
  '</div>'
)
htmltools::HTML(html_code)
```
:::
:::

::: grid
::: g-col-12
```{r}

highchart() %>%
  hc_chart(type = "line") %>%
  hc_xAxis(categories = goldmark_cumsum$formatted_month) %>%
  hc_yAxis(min = 0) %>% 
  hc_add_series(data = goldmark_cumsum$cumulative_weight, name = "Pounds", x = goldmark_cumsum$formatted_month) %>%
  hc_title(text = "Cumulative Weight of Impact") %>%
  hc_subtitle(text = "by Goldmark Cultural Center") %>%
  hc_tooltip(pointFormat = "{series.name}: {point.y:2f}") %>%
  hc_colors(palette_cpal_main) %>%
  hc_plotOptions(series = list(
    lineWidth = 4,  
    marker = list(
      enabled = TRUE,
      symbol = "circle", 
      radius = 6,         
      fillColor = NULL,   
      lineWidth = 2,
      lineColor = NULL    
    )
  )) |> 
  hc_legend(enabled = FALSE)

```
:::
:::

### Pop Up Comfortt

::: grid
::: g-col-12
```{=html}
<p style="text-align: center;font-weight: bold;">Contributions of Pop Up Comfortt</p>
```
:::
:::

::: grid
::: g-col-3
```{r}
pc_lbs_trash <- formatC(pc_lbs_trash, format = "d", big.mark = ",")
html_code <- paste0(
  '<div style="display: flex; flex-direction: column; align-items: center; height: 150px; border: 1px solid #042d33; border-radius: 5px; background-color: #042d33; color: white; position: relative;">',
  '<div style="position: absolute; top: 15%; width: 100%; display: flex; flex-direction: column; align-items: center;">',
  '<div style="display: flex; align-items: center; font-size: 2em; font-weight: bold;">', 
  pc_lbs_trash, 
  '<span style="font-size: 1.25em; margin-left: 10px;">', bsicons::bs_icon("trash"), '</span></div>',
  '</div>',
  '<div style="position: absolute; bottom: 20px; width: 100%; text-align: center;">Pounds of Trash Removed</div>',
  '</div>'
)
htmltools::HTML(html_code)
```
:::

::: g-col-3
```{r}
pc_lbs_produce <- formatC(pc_lbs_produce, format = "d", big.mark = ",")
html_code <- paste0(
  '<div style="display: flex; flex-direction: column; align-items: center; height: 150px; border: 1px solid #042d33; border-radius: 5px; background-color: #042d33; color: white; position: relative;">',
  '<div style="position: absolute; top: 15%; width: 100%; display: flex; flex-direction: column; align-items: center;">',
  '<div style="display: flex; align-items: center; font-size: 2em; font-weight: bold;">', 
  pc_lbs_produce, 
  '<span style="font-size: 1.25em; margin-left: 10px;">', bsicons::bs_icon("basket2"), '</span></div>',
  '</div>',
  '<div style="position: absolute; bottom: 20px; width: 100%; text-align: center;">Pounds of Produce Distributed</div>',
  '</div>'
)
htmltools::HTML(html_code)
```
:::

::: g-col-3
```{r}
pc_average_people_served <- formatC(pc_people_served, format = "d", big.mark = ",")
html_code <- paste0(
  '<div style="display: flex; flex-direction: column; align-items: center; height: 150px; border: 1px solid #042d33; border-radius: 5px; background-color: #042d33; color: white; position: relative;">',
  '<div style="position: absolute; top: 15%; width: 100%; display: flex; flex-direction: column; align-items: center;">',
  '<div style="display: flex; align-items: center; font-size: 2em; font-weight: bold;">', 
pc_people_served, 
  '<span style="font-size: 1.25em; margin-left: 10px;">', bsicons::bs_icon("person"), '</span></div>',
  '</div>',
  '<div style="position: absolute; bottom: 20px; width: 100%; text-align: center;">Individuals Served at Produce Drives</div>',
  '</div>'
)
htmltools::HTML(html_code)
```
:::

::: g-col-3
```{r}
html_code <- paste0(
  '<div style="display: flex; flex-direction: column; align-items: center; height: 150px; border: 1px solid #042d33; border-radius: 5px; background-color: #042d33; color: white; position: relative;">',
  '<div style="position: absolute; top: 15%; width: 100%; display: flex; flex-direction: column; align-items: center;">',
  '<div style="display: flex; align-items: center; font-size: 2em; font-weight: bold;">', 
  pc_events, 
  '<span style="font-size: 1.25em; margin-left: 10px;">', bsicons::bs_icon("hammer"), '</span></div>',
  '</div>',
  '<div style="position: absolute; bottom: 20px; width: 100%; text-align: center;">D.I.C.E Events Supported</div>',
  '</div>'
)
htmltools::HTML(html_code)
```
:::
:::

::: grid
::: g-col-12
```{r}
highchart() %>%
  hc_chart(type = "line") %>%
  hc_xAxis(categories = pop_up_cumsum$formatted_month) %>%
  hc_yAxis(min = 0) %>% 
  hc_add_series(data = pop_up_cumsum$cumulative_weight, name = "Pounds", x = pop_up_cumsum$formatted_month) %>%
  hc_title(text = "Cumulative Weight of Impact") %>%
  hc_subtitle(text = "by Pop Up Comfortt") %>%
  hc_tooltip(pointFormat = "{series.name}: {point.y:2f}") %>%
  hc_colors(palette_cpal_main) %>%
  hc_plotOptions(series = list(
    lineWidth = 4,  
    marker = list(
      enabled = TRUE,
      symbol = "circle", 
      radius = 6,         
      fillColor = NULL,   
      lineWidth = 2,
      lineColor = NULL    
    )
  )) |> 
  hc_legend(enabled = FALSE)


```
:::
:::
:::
:::
:::

```{=html}
<button id="download-pdf" class="print-button">Download PDF</button>
```
::: column-margin
Cumulative Weight of Impact combines weight of produce distributed and trash removed.
:::
